A Survey on Ordered Binary Decision Diagrams

### 2015-09-15 paper.tex
Add model checking algorithms intro

 \tbr

>>>>

Finally, after defining the $\mu$-Calculus formally, the model checking algorithms
can be described. They operate on the limited Boolean domain, i.e.
$D = \lbrace 0, 1 \rbrace$ but Burch et al.~\cite{BURCH90} also described how any
\textit{finite} domain can be encoded into this limited Boolean domain. This last
fact generalizes the introduced algorithms to any \textit{finite} domain. \tbr
